---
title: "USPriceIndex"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{USPriceIndex}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
  out.width = "100%"
```
# USpriceIndex Package

This package is a package combining the Price Index based on web scrapping information created in the paper “The Billion Prices Project: Using Online Data for Measurement and Research” – Journal of Economic Perspectives,31(1) with the official consumer price index released by US government. 

The PriceStats (PS) index is released online in csv form for scholars to replicate this research  via Harvard/MIT Dataverse:

https://dataverse.harvard.edu/file.xhtml?persistentId=doi:10.7910/DVN/6RQCRS/KGU8B0&version=2.0

The official CPI data can be accessed through Bureau of labor statistics and the documentation for this API is as follows:

https://www.bls.gov/developers/api_signature_v2.htm

It contains 2 datasets:
    
    US_price_indexes: It contains Daily price indexes in US from 2008.07-2015.08 from the sources above.
    US_price_month: It contains monthly price indexes in US from 2008.07-2015.08 from the sources above.

## Example

This is a basic demonstration of the dataset:

```{r}
# To use this package, please use library()
library(USPriceIndex)
```

Here are the basic demostration of the datasets:
```{r}
head(US_price_indexes)
head(US_price_month)
```

## data visualization
```{r}
library(ggplot2)
ggplot() + 
  geom_line(data = US_price_month, aes(x = mdate, y = PS_month), color = "blue") +
  geom_line(data = US_price_month, aes(x = mdate, y = CPI), color = "red") +
  xlab('months') +
  ylab('Price indexes number')
```

This graph compares the online price index with the official CPI. This graph shows that online price index is relatively higher than official CPI.

```{r}
library(ggplot2)
ggplot() + 
  geom_line(data = US_price_month, aes(x = mdate, y = inflation_CPI), color = "blue") +
  geom_line(data = US_price_month, aes(x = mdate, y = inflation_PS), color = "red") +
  xlab('months') +
  ylab('inflation')
```

This graph shows that online price index is quite close to official CPI. 
